SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-05 docs/questioning.tex
multiple corrections in Section 4

Code injection attacks can be divided into two categories. The first
involves binary code and the second executable source code. An
extensive survey on binary code injection attacks can be found
in~\cite{LC03}. Specific advances in exploiting such vulnerabilities
(i.e. ``heap smashing", ``arc injection" and others) have been
presented in~\cite{PB04}. The countermeasures used to detect such
defects have already been surveyed~\cite{YJP12} (many of them are also
included in a book:~\cite{DKZ12} -- Section 13.8). In the present work
we do not include binary code injection, focusing instead on defenses
that protect applications against application attacks based on the
executable source code injection category.

@@

Figure~\ref{fig:defenses} presents a taxonomy of the
defenses that protect web applications against attacks based on
code injection vulnerabilities.
We can identify three main approaches, namely:
{\it design-based}, {\it behavior-based} and {\it hybrid}.
The design-based category involves mechanisms that make applications
immune to different attack vectors by design~\cite{JL75,L81}. 
The behavior-based incorporates a variety of methods and
schemes that inspect the behavior of applications
and detect attacks based on specific criteria~\cite{D76,A00}.
Hybrid mechanisms borrow characteristics from both categories.
Table~\ref{tab:comp} groups the various subcategories
and for every mechanism provides the following:

@@

Finally, as we mentioned in Subsection~\ref{sec:model},
Figure~\ref{fig:attacks} illustrates the point where
mechanisms detect attacks.

@@

The key idea behind this approach, is to compare
the tree representation of the abstract syntactic
structure of the executable source code
with the one that was originally intended.
If the trees diverge, the application is probably
under attack.

In the case of {\sc dsl} injection attacks, mechanisms check 
the query before the inclusion of user input with the one
resulting after the inclusion of user input.
Both mechanisms that implement this approach,
{\sc sqlg}uard~\cite{BWS05} and
{\sc sql}check~\cite{SW06} are pretty similar
and detect the attack before a query reaches the
database (locus {\sc z}).
Contrary to {\sc sqlg}uard~\cite{BWS05} (and many other
mechanisms), {\sc sql}check~\cite{SW06} has been
extensively tested in terms of diagnostic performance
as seen in Table~\ref{tab:comp}. A disadvantage of
those mechanisms is that the application must be modified
every time a query is about to be sent to a database
for execution.

@@

@@

{\it Noxes}~\cite{KKVJ06,KJKV09} is the only
framework that partially allows the web
user to specify policies to prevent {\sc xss} attacks.
The key idea behind Noxes is to parse
the {\sc html} that reaches the browser to
find static {\sc url} references. Then, based on
a set of policies it allows or blocks
the request (locus {\sc x}). Such policies
are provided either by the user or by
the framework itself. Noxes does not
deal with JavaScript-driven {\sc xss}
attacks and it is a rather simplistic approach.

@@

Another policy enforcement approach introduces
policies directly either in {\sc html} or JavaScript code
to confine their behavior. {\it BrowserShield}~\cite{RDWDE07}
acts as a proxy on the server side (locus {\sc y}) to
parse the {\sc html} of server responses and identifies
scripts. Then, it rewrites them into safe equivalents
and protect the web user from exploitations
that are based on reported browser vulnerabilities.
{\it ConScript}~\cite{ML10}, {\it CoreScript}~\cite{YCIS07}
and the framework by {\it Phung et al.}~\cite{PSC09}
extend JavaScript with new primitive functions to
provide safe methods to protect potentially vulnerable
JavaScript functions. In both cases, policy enforcement takes
place on the JavaScript engine of the browser (locus {\sc x}).
In this way, {\sc xxs} attacks that take advantage
functions like {\tt eval} and {\tt write} that are
used to assemble innocuous-looking parts into harmful
strings would fail.

A critical issue regarding
the above frameworks is that they cannot
define policies that restrict the behavior of third-party
scripts introduced by script inclusion and {\tt iframe}
tags. For instance, consider a web page ({\tt foo.net})
that prints the value of the a query parameter ({\tt query})
from the page's {\sc url} in the web page's content
without escaping the value. A malicious user
can take advantage of this and inject an {\tt iframe}
into the page to steal the user's cookie and
send it via an image request to a web site
that he or she controls ({\tt malicious.com}).
This could be achieved by including the following
link to the malicious web site (or send it via phishing
email) and induce the user to click on it:

@@

Most of the aforementioned frameworks, involve
several deployment issues since they
require significant source modifications by the web
developers in order to introduce policies.

@@

{\sc isr} is a method that has been applied to counter
different kinds of application attacks~\cite{K09b,KKP03}.
The main idea behind the it, is to
separate code from data by randomizing the legitimate code's 
execution environment. In this way, the malicious code
injected by the attackers who do not know the randomization
algorithm, will not get executed.

{\it {\sc sql}rand}~\cite{BK04} is based on {\sc isr}
to detect {\sc sql} injections in the following manner:
initially, it allows programmers to create {\sc sql} statements
using randomized instructions instead of standard keywords.
The modified queries are reconstructed at runtime using
the same key that is inaccessible to the malicious user.
{\sc sql}rand is one of the few mechanisms that
detect {\sc sql} injection attacks on the database
level (locus $\Omega$).

In the case of {\sc xss} attacks that are based on JavaScript
or {\sc html}, consider a {\sc xor} function that encodes all source of a web
page on the server-side and then, on the client-side, the web browser decodes the
source by applying the same function again (locus {\sc x}).
Variations of this approach include:
{\it Noncespaces}~\cite{GC09} and {\it x{\sc js}}~\cite{APKLM10}
which randomize the instruction set of {\sc html} and
JavaScript respectively.
Contrary to x{\sc js}, in Noncespaces administrators must set
specific policies in a manner similar to a firewall
configuration language. This brings up questions
concerning the diagnostic performance of the mechanism
since the corresponding testing is insufficient
(see Table~\ref{tab:comp}).
{\it {\sc sm}ask}~\cite{JB07} is another framework
that was inspired by {\sc isr}. To detect {\sc xss}
attacks it searches for {\sc html} and JavaScript
keywords within the application's legitimate code.
This is done before the processing of an {\sc http}
request. When it finds one it adds a token to it.
This results to a ``code mask". Then,
before sending the resulting {\sc html} data to the
web user, the framework searches the data for
illegal code by using the same keywords (locus {\sc y}).
Since all legitimate code has been ``masked",
the injected code can be identified.
The pre- and post-processing of the code though,
may add a significant overhead to the application.
Unfortunately, the authors of {\sc sm}ask
did not provide measurements regarding the
computational performance of the tool (see Table~\ref{tab:comp}).

@@

There are different implementations of these approach
in terms of how the tainted data is marked and observed,
and how attacks are detected.
For example, {\it Haldar et al.}~\cite{HCF05} have implemented
their scheme for the Java Virtual Machine ({\sc jvm})
where they instrument various classes. When a
tainted string is used as an argument to a sink method
then an exception is raised (locus {\sc z}).
However, this is a simplistic approach that may
lead to many false positives.
The following schemes apply further checks when
they identify that tainted data have reached a sink
(locus {\sc z}).
In particular, {\it Xu et al.}~\cite{XBS06}
tracks taint information at the level of bytes in memory.
To distinguish between legitimate and malicious uses
of untrusted data that reach a sink,
they search the data for suspicious symbols by using
regular expressions. {\sc csse}~\cite{PB05} associates
tainted data with specific metadata. Such metadata include
the origins of tainted data, its propagation within the application
and other. When tainted data reaches a sink {\sc csse} performs
syntactic checks it based on the aforementioned metadata
(locus {\sc z}). {\it {\sc php} Aspis}~\cite{PMP11} works
in a similar way. To obtain metadata, it takes advantage
of specific features provided by {\sc php}.
% Note that the above schemes detect potential attacks
% in locus {\sc z}. This automatically means that they
% cannot detect non-persistent JavaScript-driven
% {\sc xss} attacks. Although they can be
% modified to do so.
{\sc wasc}~\cite{NLC07} analyzes {\sc html} responses to check
if there are tainted data that contain scripts (locus {\sc y}).
A recent study showed that there are ways to circumvent
the majority of the above schemes~\cite{NBR14}.
Furthermore, most of them are hard to deploy since
the majority of input vectors, string operations
and output vectors must be instrumented.

{\it Vogt et al.}~\cite{VFJKKV07}
have developed a tainting scheme that follows a different
approach. Contrary to the aforementioned schemes that
operate on the server side, they track taint sensitive
information on the client side (locus {\sc x}).
This is a form of positive taint tracking, where
taint data is considered to be legitimate.
Their scheme detects JavaScript-driven {\sc xss}
attacks by ensuring that a script can send sensitive
user data only to the site from which it came from.
This though, may lead to false alarms.
{\it Stock et al.}~\cite{SLMS14} propose a scheme
that also operates in the browser (locus {\sc x}).
The scheme focuses on the detection of
{\sc dom}-based {\sc xss} attacks.
In such an attack, the malicious payload is
executed as a result of the modification of the
{\sc dom} environment so that the client-side
code runs in an unanticipated manner even if the
{\sc http} response that triggers the injection seems legitimate.
The scheme is different to the previous one because it
marks and observes data that are considered harmful.
Specifically, it employs a taint-enhanced JavaScript
engine that tracks the flow of attacker-controlled data.
To detect potential attacks the scheme utilizes
{\sc html} and JavaScript parsers that can
identify the generation of code coming from
tainted data.

@@

Training techniques are based on the ideas of Denning's original
intrusion detection framework~\cite{Den87}. In particular, a training
mechanism registers all valid legitimate code statements during a
training phase, most of the time in the form of signatures. This can
be done in various ways according to the implementation. Then, only
those will be accepted, approved or recognized during production.

@@

{\sc xss-guard}~\cite{BV08} is a training scheme
that also employs parse-tree validation.
During training, the scheme maps legitimate scripts
to {\sc http} responses. During production
{\sc xss-guard} retrieves for every script included
in a response its parse-tree and checks if it
is one of those previously mapped to this response.
Apart from the comparison of the parsed-trees, {\sc xss-guard}
checks also for an exact match of lexical entities.
To achieve this, the scheme utilizes that data structures
of Firefox's JavaScript engine (locus {\sc x}).
However, string literals are not compared literally
thus, a possible false negative result could occur if an
adversary performed a mimicry attack~\cite{WS02}.
For example, consider a banner rotator that
every time it runs, it creates a value that depends on
the current date and the length of the array that
contains the references of the various images to be displayed.
Then, based on this value it shows a specific
image to a user. In a vulnerable web site that allows
users to post data and contains this banner
rotator, a malicious user could create and store a script
that has the same code structure, with the same JavaScript
keywords like the above. In this script the
attacker could also include references to tiny
images hosted on a web server that is maintained by him in order
to retrieve the {\sc ip} addresses of the
users that visit the vulnerable site.

{\it Blueprint}~\cite{LV09} is a policy
enforcement framework that also utilizes parsed-trees
to detect {\sc xss} attacks. To guarantee
that untrusted content is not executed, Blueprint generates
on the server-side a parse-tree from untrusted {\sc html}
to ensure that it does not contain any dynamic content.
Then the parsed-tree is transfered to the document
generator of the browser (locus {\sc x}) where untrusted
browser parsing behavior is ruled out.
Blueprint is an efficient countermeasure but it
imposes a significant overhead due to its
extensive parsing (see Table~\ref{tab:comp}).

{\it Diglossia}~\cite{SMS13} combines positive taint tracking
(see Subsubsection~\ref{sec:taint}) together with
parse-tree validation. Diglossia was based on the
theory of Ray and Ligatti~\cite{RL12b} (also see
Section~\ref{sec:attacks}) to detect {\sc dsl}
code injection attacks. In addition, it is actually
the first, and so far the only framework that detects
No{\sc sql} injection attacks.
When an application computes an output string (query),
Diglossia computes a ``shadow" of this string.
Specifically, it maps all characters introduced by
the application to a shadow character set.
This set does not contain any characters coming
from the tainted input. Then, the scheme
creates the parse-tree of the query that
is about to be executed with the parse-tree
of the ``shadow" and compares them (locus {\sc z}).
If the trees are not equal the application is probably
under attacks. Diglossia can be bypassed in the same
way as other taint tracking approaches~\cite{NBR14}.

@@

% Comment: The above are some extra findings that
% indicate that there is no standard way to
% test such mechanisms. Perhaps, forming a
% standard way to test such tools in terms
% of diagnostic and computational performance
% would be one of the reasons of adopting them.

@@

Notes:
\begin{enumerate}
\item Note that most mechanisms that implement design-based
approaches have not been extensively tested in terms of
diagnostic performance.
\item We need to mention that there are mechanisms that
do not need to be established purely through testing
Since they provide systematic arguments as to why
the design is secure against attacks.
\item Policy enforcement is the
only approach that is
used to prevent {\sc csrf} attacks.
\item See j{\sc csrf} for {\sc soma}'s drawbacks.
\end{enumerate}

>>>>

Code injection attacks can be divided into two categories. The first
involves binary code and the second executable source code. An
extensive survey on binary code injection attacks can be found
in~\cite{LC03}. Specific advances in exploiting such vulnerabilities
(i.e. ``heap smashing", ``arc injection" and others) have been
presented in~\cite{PB04}. The countermeasures used to detect such
defects have already been surveyed~\cite{YJP12} (many of them are also
included in a book:~\cite{DKZ12} -- Section 13.8). In the present work
we do not include binary code injection, focusing instead on defenses
that protect applications against attacks based on the
executable source code injection category.

@@

Figure~\ref{fig:defenses} presents a taxonomy of the
defenses that protect web applications against attacks based on
code injection vulnerabilities.
We can identify three approaches, namely:
{\it design-based}, {\it behavior-based} and {\it hybrid}.
The design-based category involves mechanisms that make applications
immune to different attack vectors by design~\cite{JL75,L81}. 
The behavior-based category incorporates a variety of
schemes that inspect the behavior of applications
and detect attacks based on specific criteria~\cite{D76,A00}.
Hybrid mechanisms borrow characteristics from both categories.
Table~\ref{tab:comp} groups the various subcategories
and for every mechanism provides the following:

@@

Finally, as we mentioned in Subsection~\ref{sec:model},
Figure~\ref{fig:attacks} illustrates for each mechanism
(found in the figure's caption), the point where
it detects attacks.

@@

The key idea behind this approach, is to compare
the tree representation of the abstract syntactic
structure of the source code that is about to be
executed with the one that was originally intended.
If the trees diverge, the application is probably
under attack.

In the case of {\sc dsl} injection attacks, mechanisms check 
the query before the inclusion of user input with the one
resulting after the inclusion of user input.
Both mechanisms that implement this approach,
{\sc sqlg}uard~\cite{BWS05} and
{\sc sql}check~\cite{SW06} are pretty similar
and detect the attack before a query reaches the
database (locus {\sc z}).
Contrary to {\sc sqlg}uard (and other
mechanisms as we sill observe), {\sc sql}check has been
extensively tested in terms of diagnostic performance
as it can be seen in Table~\ref{tab:comp}.
A disadvantage of those mechanisms is that the
application must be modified in every code fragment
that sends an {\sc sql} query to the database for execution.

@@

Parse-tree validation seems to be an efficient approach
to detect {\sc dsl} code injection attack,
especially in the case of the {\sc sql}check
implementation. This however does not apply in
the case of the mechanisms that utilize
this approach to detect JavaScript-driven {\sc xss} attacks
as we will see in Subsection~\ref{sec:hybrid}.

@@

{\it Noxes}~\cite{KKVJ06,KJKV09} is the only
framework that partially allows the web
user to specify policies to prevent {\sc xss} attacks.
The key idea behind Noxes is to parse
the {\sc html} that reaches the browser to
find static {\sc url} references. Then, based on
a set of policies Noxes allows or blocks
the request (locus {\sc x}). Such policies
can be also provided by the server (i.e. ``never
follow a link that leads to the malicious.com
web site"). Noxes does not deal with
JavaScript-driven {\sc xss} attacks and it is a rather
simplistic approach.

@@

Another policy enforcement approach introduces
policies directly either in {\sc html} or JavaScript code
to confine their behavior. {\it BrowserShield}~\cite{RDWDE07}
acts as a proxy on the server side (locus {\sc y}) to
parse the {\sc html} of server responses and identifies
scripts. Then, it rewrites them into safe equivalents
and protect the web user from exploitations
that are based on reported browser vulnerabilities.
{\it ConScript}~\cite{ML10}, {\it CoreScript}~\cite{YCIS07}
and the framework by {\it Phung et al.}~\cite{PSC09}
extend JavaScript with new primitive functions that
provide safe methods to protect potentially vulnerable
JavaScript functions. In both cases, policy enforcement takes
place on the JavaScript engine of the browser (locus {\sc x}).
In this way, {\sc xxs} attacks that take advantage
functions like {\tt write} and {\tt eval}, which are
used to assemble innocuous-looking parts into harmful
strings,\footnote{The infamous Sammy worm that
infected MySpace in 2005~\cite{SP07,ELX07}
utilized the {\tt eval} function to assemble a
script with malicious behavior.} would fail.

A critical issue regarding
the above frameworks is that they cannot
define policies that restrict the behavior of third-party
scripts introduced by script inclusion and {\tt iframe}
tags. For instance, consider a web page (foo.net)
that prints the value of a query parameter ({\tt query})
from the page's {\sc url} in the web page's content
without escaping the value. A malicious user
can take advantage of this and inject an {\tt iframe}
into the page to steal the user's cookie and
send it via an image request to a web site
that he or she controls (malicious.com).
This could be achieved by including the following
link to the malicious web site (or send it via phishing
email) and induce the user to click on it:

@@

Most of the aforementioned frameworks, involve
several deployment issues since they
require significant source modifications by the
developers on the server-side, in order to
introduce the policies.

@@

{\sc isr} is a method that has been applied to counter
different kinds of application attacks~\cite{K09b,KKP03}.
The main idea behind it, is to separate code from
data by randomizing the legitimate code's 
execution environment. In this way, the malicious code
injected by the attackers who do not know the randomization
algorithm, will not get executed.

{\it {\sc sql}rand}~\cite{BK04} implements {\sc isr}
to detect {\sc sql} injection attacks. It works in the following manner:
initially, it allows programmers to create {\sc sql} statements
using randomized instructions instead of standard keywords.
The modified queries are reconstructed at runtime using
the same key that is inaccessible to the malicious user.
{\sc sql}rand is one of the few mechanisms that
detect {\sc sql} injection attacks on the database
level (locus $\Omega$).

In the case of {\sc xss} attacks that are based on JavaScript
or {\sc html}, consider a {\sc xor} function that encodes all source of a web
page on the server-side and then, on the client-side, the web browser decodes the
source by applying the same function again (locus {\sc x}).
Variations of this approach include:
{\it Noncespaces}~\cite{GC09} and {\it x{\sc js}}~\cite{APKLM10}
which randomize the instruction set of {\sc html} and
JavaScript respectively.
Contrary to x{\sc js}, in Noncespaces administrators must set
specific policies in a manner similar to a firewall
configuration language. This fact, together with the
insufficient testing of the mechanism (see Table~\ref{tab:comp})
brings up questions concerning its diagnostic performance.
{\it {\sc sm}ask}~\cite{JB07} is another framework
that was inspired by {\sc isr}. To detect {\sc xss}
attacks it searches for {\sc html} and JavaScript
keywords within the application's legitimate code.
This is done before the processing of an {\sc http}
request. When it finds one it adds a token to it.
This results to a ``code mask". Then,
before sending the resulting {\sc html} data to the
web user, the framework searches the data for
illegal code by using the same keywords (locus {\sc y}).
Since all legitimate code has been ``masked",
the injected code can be identified.
The pre- and post-processing of the code though,
may add a significant overhead to the application.
Unfortunately, the authors of {\sc sm}ask
did not provide measurements regarding the
computational performance of the tool (see Table~\ref{tab:comp}).

@@

There are different implementations of this approach
in terms of how the tainted data is marked and observed,
and how attacks are detected.
For example, {\it Haldar et al.}~\cite{HCF05} have implemented
their scheme for the Java Virtual Machine ({\sc jvm})
where they instrument various classes. When a
tainted string is used as an argument to a sink method
then an exception is raised (locus {\sc z}).
However, this is a simplistic approach that may
lead to many false positives.

The following schemes apply further checks when
they identify that tainted data have reached a sink
(locus {\sc z}).
In particular, {\it Xu et al.}~\cite{XBS06}
tracks taint information at the level of bytes in memory.
To distinguish between legitimate and malicious uses
of untrusted data that reach a sink,
they search the data for suspicious symbols by using
regular expressions. {\sc csse}~\cite{PB05} associates
tainted data with specific metadata. Such metadata include
the origins of tainted data, its propagation within the application
and others. When tainted data reaches a sink {\sc csse} performs
syntactic checks based on the aforementioned metadata
(locus {\sc z}). {\it {\sc php} Aspis}~\cite{PMP11} works
in a similar way. To obtain metadata, it takes advantage
of specific features provided by {\sc php}.
% Note that the above schemes detect potential attacks
% in locus {\sc z}. This automatically means that they
% cannot detect non-persistent JavaScript-driven
% {\sc xss} attacks. Although they can be
% modified to do so.
Finally, {\sc wasc}~\cite{NLC07} analyzes {\sc html} responses to check
if there are tainted data that contain scripts (locus {\sc y}).
A recent study showed that there are ways to circumvent
the majority of the above schemes~\cite{NBR14}.
Furthermore, most of them are not easy to deploy since
the majority of input vectors, string operations
and output vectors of the application must be instrumented.

{\it Vogt et al.}~\cite{VFJKKV07}
have developed a tainting scheme that follows a different
approach. Contrary to the aforementioned schemes that
operate on the server side, they track sensitive
information on the client side (locus {\sc x}).
This is a form of positive taint tracking, where
taint data is considered to be legitimate.
Their scheme detects JavaScript-driven {\sc xss}
attacks by ensuring that a script can send sensitive
user data only to the site from which it came from.
This though, may lead to false alarms.
{\it Stock et al.}~\cite{SLMS14} propose a scheme
that also operates in the browser (locus {\sc x}).
The scheme focuses on the detection of
{\sc dom}-based {\sc xss} attacks.
In such an attack, the malicious payload is
executed as a result of the modification of the
{\sc dom} environment so that the client-side
code runs in an unanticipated manner even if the
{\sc http} response that triggers the injection seems legitimate.
The scheme is different from the previous one because it
marks and observes data that are considered harmful.
Specifically, it employs a taint-enhanced JavaScript
engine that tracks the flow of attacker-controlled data.
To detect potential attacks the scheme utilizes
{\sc html} and JavaScript parsers that can
identify the generation of code coming from
tainted data.

@@

Training techniques are based on the ideas of Denning's original
intrusion detection framework~\cite{Den87}. In particular, a training
mechanism registers all valid legitimate code statements during a
training phase (mostly in the form of signatures). This can
be done in various ways according to the implementation. Then, only
those will be recognized and approved for execution
during production.

@@

{\sc xss-guard}~\cite{BV08} is a training scheme
that also employs parse-tree validation.
During training, the scheme maps legitimate scripts
to {\sc http} responses. During production
{\sc xss-guard} retrieves for every script included
in a response its parsed tree and checks if it
is one of those previously mapped to this response.
Apart from the comparison of the parsed trees, {\sc xss-guard}
checks also for an exact match of lexical entities.
To achieve this, the scheme utilizes that data structures
of Firefox's JavaScript engine (locus {\sc x}).
However, string literals are not compared literally
thus, a possible false negative result could occur if an
adversary performs a mimicry attack~\cite{WS02}.
For example, consider a banner rotator that
every time it runs, it creates a value that depends on
the current date and the length of the array that
contains the references of the various images to be displayed.
Then, based on this value it shows a specific
image to a user. In a vulnerable web site that allows
users to post data and contains this banner
rotator, a malicious user could create and store a script
that has the same code structure, with the same JavaScript
keywords like the above. In this script the
attacker could also include references to tiny
images hosted on a web server that is maintained by him in order
to retrieve the {\sc ip} addresses of the
users that visit the vulnerable site.

{\it Blueprint}~\cite{LV09} is a policy
enforcement framework that also utilizes parsed trees
to detect {\sc xss} attacks. To guarantee
that untrusted content is not executed, Blueprint generates
on the server-side a parsed tree from untrusted {\sc html}
to ensure that it does not contain any dynamic content.
Then the parsed tree is transfered to the document
generator of the browser (locus {\sc x}) where untrusted
browser parsing behavior is ruled out.
Blueprint is an efficient countermeasure but it
imposes a significant overhead due to its
extensive parsing (see Table~\ref{tab:comp}).

{\it Diglossia}~\cite{SMS13} combines positive taint tracking
(see Subsubsection~\ref{sec:taint}) together with
parse-tree validation. Diglossia was based on the
theory of Ray and Ligatti~\cite{RL12b} (also see
Section~\ref{sec:attacks}) to detect {\sc dsl}
code injection attacks. In addition, it is actually
the first, and so far the only framework that detects
No{\sc sql} injection attacks.
When an application computes an output string (query),
Diglossia computes a ``shadow" of this string.
Specifically, it maps all characters introduced by
the application to a shadow character set.
This set does not contain any characters coming
from the tainted input. Then, the scheme
creates the tree of the query that
is about to be executed and compares it with the parsed tree
of the ``shadow" (locus {\sc z}).
If the trees are not equal the application is probably
under attack. Note that, Diglossia can be bypassed in the same
way as other taint tracking approaches~\cite{NBR14}.

@@

% Comment 1: Regarding the frameworks that were
% not tested in terms of diagnostic performance
% at all, we see that they are mostly coming from
% the design-based category.

% Comment 2: Note though that implementations
% of design-based mechanisms can actually
% be bypassed.

% Comment 3: The above are some extra findings that
% indicate that there is no standard way to
% test such mechanisms. Perhaps, forming a
% standard way to test such tools in terms
% of diagnostic and computational performance
% would be one of the reasons of adopting them.

@@

Notes:
\begin{enumerate}
\item Note that most mechanisms that implement design-based
approaches have not been extensively tested in terms of
diagnostic performance.
\item We need to mention that there are mechanisms that
do not need to be established purely through testing
Since they provide systematic arguments as to why
the design is secure against attacks.
\item Policy enforcement is the
only approach that is
used to prevent {\sc csrf} attacks.
\item See j{\sc csrf} for {\sc soma}'s drawbacks.
\item Discuss about how tools can be easily modified
to detect other attacks ({\sc sql}rand).
\end{enumerate}
